\documentclass{beamer}
\title {Project Excalibur - Blockchain for Computing}
\author{Joseph Chen-Yu~Wang}
\institute{In association with the Banzai Institute of Advanced Research\\
  and the Hong Kong Caviliers}
\date{\today}
\usetheme{Dresden}
\usecolortheme{beaver}
\setlength{\parskip}{\baselineskip}
\begin{document}
\frame{\titlepage}
\begin{frame}
  \frametitle{About me}
Professional supercomputer babysitter.  Ph.D. in computational
astrophysics, worked as a quant in parallel computing 
infrastructure at JPMorgan.
\end{frame}
\begin{frame}
  \frametitle{Big computing is big business}
  \begin{itemize}
  \item Big data analytics to hit USD 200 billion by 2020
  \item Video gaming industry - USD 150 billion by 2020
  \item Algotrading AUM - Hundreds of billions
  \item Not counting AI and other breakthrough uses
  \item Multi-trillion dollar industry
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{But we are in the stone age when it comes to computing}
  \begin{itemize}
  \item Standard computing architectures
  \item We are using CPU designs from the 1990's
  \item We are running into basic hardware limits
  \item Quantum computing?  FPGA? Special purpose hardware?
  \end{itemize}
\end{frame} 
\begin{frame}
  \frametitle{Who is doing something really different?}
  \begin{itemize}
  \item BITCOIN!!!!
  \item Bitcoin mining network does 40,000 exaflops
  \item Worlds fastest supercomputer in 2020 will do 1(!) exaflop
  \item How do we take the bitcoin architecture and put it into
    general purpose computing
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{The Basic Idea}
  \begin{itemize}
  \item I have a math problem.
  \item If you solve the math problem.  I will give cash to the first
    person that solves the problem.
  \item I don't care how you solve the math problem.
  \item I use blockchain verify that you have the right
    solution, and that you get the cash.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{The competition is doing it wrong}
  \begin{itemize}
    \item People have raised USD 8 million for ICO's and they are
      doing it wrong
    \item People are thinking about selling CPU power and not
      math solutions.
    \item I can't hook up my quantum, space alien math problem solver
      to their network
    \item People are trying to compete with the big number crunchers.
      I want to give them a new source of revenue
    \item Create the network, and Amazon, Alibaba, Microsoft, and IBM
      just plug right in
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Security and privacy}
  \begin{itemize}
  \item I'm adding two numbers
  \item You don't easily know *why* I am adding two numbers
  \item I can hide the math problem.  I want to add two numbers.  I add
    random numbers to the problem I send to the network and have it
    solve a disguised problem
  \item Or I just download the system and run it on my internal
    corporate network
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Where is the toll booth}
  \begin{itemize}
  \item You put in the framework for free
  \item You make money by helping business do the big data and
      corporate stuff that they normally do
  \end{itemize}
\end{frame}
\end{document}
